
 ---
title: "F Series TMP 37 Calibration"
output: html_document
date: "2024-03-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(car)
library(dplyr)
library(ggplot2)
library(ggridges)
library(datasets)
library(magrittr)
library(svglite)

```

Functions to load:
```{r}
#Function for converting volts to Celsius:
#TMP36 Sensors
VtoC36 <- function(volts) {
  celsius <- (volts - 0.5) / 0.01
  return(celsius)}

#TMP37 Sensors
VtoC37 <- function(volts) {
  celsius <- (volts / 0.02)
  return(celsius)}

#Cleaning data frame -- removing unnecessary characters, making columns numeric, and removing all NA's
clean <- function(d, a, b) {
  d <- as.data.frame(d)
  d[[a]] <- gsub(":", "", d[[a]])
  d[[b]] <- gsub(":", "", d[[b]])
  d[[a]] <- as.numeric(d[[a]])
  d[[b]] <- as.numeric(d[[b]])
  d <- na.omit(d)
  return(d)
}

#Adding an Elapsed Time column to data frame:
#TCHC 2 point calibration data 
add.time1.6 <- function(d) {
  increment <- 1.6
  num_rows <- nrow(d)
  Time <- seq(from = 0, by = increment, length.out = num_rows)
  d$Time <- Time
  return(d)
}

#ECDR Calorimeter data
add.time31.6 <- function(d) {
  increment <- 31.6
  num_rows <- nrow(d)
  Time <- seq(from = 0, by = increment, length.out = num_rows)
  d$Time <- Time
  return(d)
}

#Creating Linear Models and Saving Slope and Intercepts From Data
lm.slope.int <- function(d, x, y) {
  formula_str <- paste(y, "~", x)
  lm_form <- as.formula(formula_str)
  lm_d <- lm(lm_form, data = d)
  lmcoef <- coef(lm_d)
  slope_d <- lmcoef[x]
  intercept_d <- lmcoef["(Intercept)"]
  return(list(slope = slope_d, intercept = intercept_d))
}

#Creating a function to remove 0 values from data set
remove.zeros36 <- function(d, ...) {
  d %>%
    filter(across(..., ~ . > 0.5 & . < 0.9))
}


```

Read in data sets:
```{r}

F_Series <- read.csv("SenCal_seriesF_031124.csv")

```

Subset data for only the columns you need:
```{r}

F_Series <- F_Series[, c("CALIBRATE", "X.3", "X.5")]

```

Cleaning:
```{r}

F_Series <- clean(F_Series, "X.3", "X.5")
F_Series <- subset(F_Series, F_Series$X.5 > 0.3) #removes 0 values from data set

```

Changing names of headings:
```{r}

colnames(F_Series)[2] <- "NIST"
colnames(F_Series)[3] <- "GrefV"

```

Creating new columns converting Volts to Celsius and removing 0 value:
```{r}

F_Series$GrefC <- VtoC37(F_Series$GrefV)

```

Subseting Hi and Low:
```{r}

Lo <- subset(F_Series, CALIBRATE == "Lo")
Hi <- subset(F_Series, CALIBRATE == "Hi")

```

Create a new data frame for sorting by NIST:
```{r}

#order the data based on ascending NIST values
Lo_Sorted <- Lo[order(Lo$NIST), ]

#order the data based on ascending NIST values
Hi_Sorted <- Hi[order(Hi$NIST), ]

```

Add Elapsed Time to new sorted data frames:
```{r}

Lo_Sorted <- add.time1.6(Lo_Sorted)
Hi_Sorted <- add.time1.6(Hi_Sorted)

```

Graphing Sorted Data:
```{r}
F_TMP37_lo <- ggplot(Lo_Sorted, aes(x = Time))+
  geom_point(aes(y = GrefC, color = "Gref"))+
  geom_point(aes(y = NIST, color = "NIST"))+
  geom_smooth(aes(y = GrefC), method = "lm", se = FALSE, color = "black")+
  geom_smooth(aes(y = NIST), method = "lm", se = FALSE, color = "black")+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Time (s)", 
       y="Temperature (°C)",
       color = "Sensor")+
  annotate("text", x = 1000, y = 19.3, label = "y = 0.0003383x + 19.33")+
  annotate("text", x = 1000, y = 19, label = expression("R"^2*" = 0.9358"))+
  annotate("text", x = 1000, y = 15.8, label = "y = 0.0002707x + 15.83")+
  annotate("text", x = 1000, y = 15.5, label = expression("R"^2*" = 0.9297"))+
  scale_color_manual(name = "Sensor",
                     breaks = c('NIST', 'Gref'),
                     values = c('NIST' = 'gold4', 'Gref' = 'red'))+ 
  ggtitle("Linear Model (Low Temperature)")+
  theme_classic()

F_TMP37_lo

#ggsave("F Series TMP 37 linear model.png", F_TMP37_lo, width = 15, height = 10, units = "cm")

ggplot(Hi_Sorted, aes(x = Time))+
  geom_point(aes(y = GrefC, color = "Gref"))+
  geom_point(aes(y = NIST, color = "NIST"))+
  geom_smooth(aes(y = GrefC), method = "lm", se = FALSE, color = "black")+
  geom_smooth(aes(y = NIST), method = "lm", se = FALSE, color = "black")+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Time (s)", 
       y="Temperature (°C)",
       color = "Sensor")+
  annotate("text", x = 1600, y = 32.4, label = "y = 0.0.001135x + 31.52")+
  annotate("text", x = 1600, y = 26.5, label = "y = 0.0008599x + 26.22")+
  scale_color_manual(name = "Sensor",
                     breaks = c('NIST', 'Gref'),
                     values = c('NIST' = 'gold4', 'Gref' = 'red'))+ 
  ggtitle("NIST and Gref Sensor (High Temperature)")+
  theme_classic()
```

Slope and Intercept of the lines created in graphs:
```{r}

#making the models for the lm lines on above graph
results <- lm.slope.int(Lo_Sorted, "Time", "NIST")
slope_LNIST <- results$slope
intercept_LNIST <- results$intercept

results <- lm.slope.int(Hi_Sorted, "Time", "NIST")
slope_HNIST <- results$slope
intercept_HNIST <- results$intercept

results <- lm.slope.int(Lo_Sorted, "Time", "GrefC")
slope_LGref <- results$slope
intercept_LGref <- results$intercept

results <- lm.slope.int(Hi_Sorted, "Time", "GrefC")
slope_HGref <- results$slope
intercept_HGref <- results$intercept

```

Plug in 22 and 35 into y=mx+b from above:
```{r}
#LOW
NIST22 <- (slope_LNIST*22) + intercept_LNIST

GREF22 <- (slope_LGref*22) + intercept_LGref

#HIGH
NIST35 <- (slope_HNIST*35) + intercept_HNIST

GREF35 <- (slope_HGref*35) + intercept_HGref

#Ranges
NISTR <- NIST35 - NIST22
  
GREFR <- GREF35 - GREF22

```

Making new dataframe w these 4 points:
```{r}
T1T2 <- tibble(
  Temp = c(22, 35),
  CGref = c(GREF22, GREF35),
  CNIST = c(NIST22, NIST35)
)
```

Graph CNIST and CGREF:
```{r}
Cal_b4corrected <- ggplot(T1T2, aes(x = Temp))+
  geom_point(aes(y = CGref, color = "Gref"))+
  geom_point(aes(y = CNIST, color = "NIST"))+
  geom_smooth(aes(y = CGref), method = "lm", se = FALSE, color = "red")+
  geom_smooth(aes(y = CNIST), method = "lm", se = FALSE, color = "gold4")+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Temperature (°C)", 
       y="Temperature (°C)",
       color = "Reference")+
  scale_color_manual(name = "Reference",
                     breaks = c('NIST', 'Gref'),
                     values = c('NIST' = 'gold4', 'Gref' = 'red'))+ 
  ggtitle("NIST and Gref Before Correction")+
  theme_classic()

Cal_b4corrected

#ggsave("Cal_b4corrected.png", plot = Cal_b4corrected, width = 10, height = 6, dpi = 300)
```

Slope and Intercept of the lines created in graphs:
```{r}

#making the models for the lm lines on above graphs
results <- lm.slope.int(T1T2, "Temp", "CNIST")
slope_CNIST <- results$slope
intercept_CNIST <- results$intercept

results <- lm.slope.int(T1T2, "Temp", "CGref")
slope_CGref <- results$slope
intercept_CGref <- results$intercept

```

Finding Ultimate Gref formula:
```{r}

UCGREFL <- (((15.71795 - GREF22)*(NISTR))/GREFR) + NIST22 #used real lowest value from raw data 

UCGREFH <- (((25.62540 - GREF22)*(NISTR))/GREFR) + NIST22 #used real lowest value from raw data 

#UCREF <- (((a - 13.112233)*(9.866786))/(8.345732) + (23.0521835)
```

New data frame of CNIST and UCGREF: 
```{r}

NIST.UCGREF <- tibble(
  Temp = c(22, 35),
  CNIST = c(NIST22, NIST35),
  UCGREF = c(UCGREFL, UCGREFH), 
  CGref = c(GREF22, GREF35)
)

```

Plotting:
```{r}

F_TMP37_Cal <- ggplot(NIST.UCGREF, aes(x = Temp))+
  geom_point(aes(y = UCGREF, color = "Ref Post"))+
  geom_point(aes(y = CNIST, color = "NIST"))+
  geom_point(aes(y = CGref, color = "Ref Pre"))+
  geom_smooth(aes(y = UCGREF), method = "lm", se = FALSE, color = "black")+
  geom_smooth(aes(y = CGref), method = "lm", se = FALSE, color = "red")+
  geom_smooth(aes(y = CNIST), method = "lm", se = FALSE, color = "gold4")+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Temperature (°C)", 
       y="Temperature (°C)",
       color = "Reference")+
  scale_color_manual(name = "Sensor",
                     breaks = c('NIST', 'Ref Pre', 'Ref Post'),
                     values = c('Ref Post' = 'black', 'NIST' = 'gold4', 'Ref Pre' = 'red'))+ 
  ggtitle("Calibration of Ref to NIST Sensor")+
  theme_classic()

F_TMP37_Cal

#ggsave("F Series TMP 37 Calibration.png", F_TMP37_Cal, width = 15, height = 10, units = "cm")
```

~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

EDCR DATA:


Read in data sets:
```{r}

Exp64lo <- read.csv("CB_ECDR64_TMP37lo_3.27.24SHORT.csv")
Exp64hi <- read.csv("CB_ECDR64_TMP37hi_3.27.24.csv")

```

Subset for columns needed:
```{r}
Exp64lo <- Exp64lo[, c("ch0", "ch1", "ch2", "ch3","Gref", "ch5", "ch6", "ch7")]
Exp64hi <- Exp64hi[, c("Ch0", "Ch1", "Ch2", "Ch3", "Gref", "Ch5", "Ch6", "Ch7")]
```

Add Elapsed Time to new data frame:
```{r}
Exp64lo <- add.time31.6(Exp64lo)
Exp64hi <- add.time31.6(Exp64hi)
```

Celsius:
```{r}
Exp64lo$ch0 <- VtoC37(Exp64lo$ch0)
Exp64lo$ch1 <- VtoC37(Exp64lo$ch1)
Exp64lo$ch2 <- VtoC37(Exp64lo$ch2)
Exp64lo$ch3 <- VtoC37(Exp64lo$ch3)
Exp64lo$Gref <- VtoC37(Exp64lo$Gref)
Exp64lo$ch5 <- VtoC37(Exp64lo$ch5)
Exp64lo$ch6 <- VtoC37(Exp64lo$ch6)
Exp64lo$ch7 <- VtoC37(Exp64lo$ch7)

Exp64hi$Ch0 <- VtoC37(Exp64hi$Ch0)
Exp64hi$Ch1 <- VtoC37(Exp64hi$Ch1)
Exp64hi$Ch2 <- VtoC37(Exp64hi$Ch2)
Exp64hi$Ch3 <- VtoC37(Exp64hi$Ch3)
Exp64hi$Gref <- VtoC37(Exp64hi$Gref)
Exp64hi$Ch5 <- VtoC37(Exp64hi$Ch5)
Exp64hi$Ch6 <- VtoC37(Exp64hi$Ch6)
Exp64hi$Ch7 <- VtoC37(Exp64hi$Ch7)
```

Column for UCGref:
```{r}

Exp64lo$UCGref <- ((((Exp64lo$Gref - GREF22)*(NISTR))/GREFR) + NIST22)
Exp64hi$UCGref <- ((((Exp64hi$Gref - GREF22)*(NISTR))/GREFR) + NIST22)

```

Sort data by UCGREF:
```{r}

#order the data based on ascending NIST values
Exp64lo_Sorted <- Exp64lo[order(Exp64lo$UCGref), ]

#order the data based on ascending NIST values
Exp64hi_Sorted <- Exp64hi[order(Exp64hi$UCGref), ]

```

Add Elapsed Time to new data frame:
```{r}
Exp64lo_Sorted <- add.time31.6(Exp64lo_Sorted)
Exp64hi_Sorted <- add.time31.6(Exp64hi_Sorted)
```

Graphing Sorted data:
```{r}
ggplot(Exp64lo_Sorted, aes(x = Time))+
  geom_point(aes(y = ch0, color = "F8"))+
  geom_point(aes(y = ch1, color = "F2"))+
  geom_point(aes(y = ch2, color = "F6"))+
  geom_point(aes(y = ch3, color = "F7"))+
  geom_point(aes(y = ch5, color = "F3"))+
  geom_point(aes(y = ch6, color = "F5"))+
  geom_point(aes(y = ch7, color = "F4"))+
#  geom_point(aes(y = GrefC, color = "Ref Pre"))+
 # geom_point(aes(y = UCGref, color = "Ref Post"))+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Time (s)", 
       y="Temperature (°C)", 
       color = "Sensor")+
  scale_color_manual(name = "Sensor", 
                     breaks = c('F8', 'F2', 'F6', 'F7', 'F3', 'F5', 'F4', 'Ref Post'), 
                     values = c('F8' = 'blue', 'F2' = 'green', 'F6' = 'orange', 'F7' = 'pink', 'F3' = 'red', 'F5' = 'aquamarine4', 'F4' = 'purple', 'Ref Post' = 'black'))+
  ggtitle("Low Temperature EDCR F Series")+
  theme_classic()

ggplot(Exp64hi_Sorted, aes(x = Time))+
  geom_point(aes(y = Ch0, color = "F8"))+
  geom_point(aes(y = Ch1, color = "F2"))+
  geom_point(aes(y = Ch2, color = "F6"))+
  geom_point(aes(y = Ch3, color = "F7"))+
  geom_point(aes(y = Ch5, color = "F3"))+
  geom_point(aes(y = Ch6, color = "F5"))+
  geom_point(aes(y = Ch7, color = "F4"))+
#  geom_point(aes(y = GrefC, color = "Ref Pre"))+
  #geom_point(aes(y = UCGref, color = "Ref Post"))+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Time (s)", 
       y="Temperature (°C)", 
       color = "Sensor")+
  scale_color_manual(name = "Sensor", 
                     breaks = c('F8', 'F2', 'F6', 'F7', 'F3', 'F5', 'F4', 'Ref Post'), 
                     values = c('F8' = 'blue', 'F2' = 'green', 'F6' = 'orange', 'F7' = 'pink', 'F3' = 'red', 'F5' = 'aquamarine4', 'F4' = 'purple', 'Ref Post' = 'black'))+
  ggtitle("High Temp EDCR F Series")+
  theme_classic()
```

Slope and Intercept of the lines created in graphs:
```{r}

#making the models for the lm lines on above graph
results <- lm.slope.int(Exp64lo_Sorted, "Time", "ch0")
slope_ch0 <- results$slope
intercept_ch0 <- results$intercept

results <- lm.slope.int(Exp64lo_Sorted, "Time", "ch1")
slope_ch1 <- results$slope
intercept_ch1 <- results$intercept

results <- lm.slope.int(Exp64lo_Sorted, "Time", "ch2")
slope_ch2 <- results$slope
intercept_ch2 <- results$intercept

results <- lm.slope.int(Exp64lo_Sorted, "Time", "ch3")
slope_ch3 <- results$slope
intercept_ch3 <- results$intercept

results <- lm.slope.int(Exp64lo_Sorted, "Time", "ch5")
slope_ch5 <- results$slope
intercept_ch5 <- results$intercept

results <- lm.slope.int(Exp64lo_Sorted, "Time", "ch6")
slope_ch6 <- results$slope
intercept_ch6 <- results$intercept

results <- lm.slope.int(Exp64lo_Sorted, "Time", "ch7")
slope_ch7 <- results$slope
intercept_ch7 <- results$intercept



results <- lm.slope.int(Exp64hi_Sorted, "Time", "Ch0")
slope_Ch0 <- results$slope
intercept_Ch0 <- results$intercept

results <- lm.slope.int(Exp64hi_Sorted, "Time", "Ch1")
slope_Ch1 <- results$slope
intercept_Ch1 <- results$intercept

results <- lm.slope.int(Exp64hi_Sorted, "Time", "Ch2")
slope_Ch2 <- results$slope
intercept_Ch2 <- results$intercept

results <- lm.slope.int(Exp64hi_Sorted, "Time", "Ch3")
slope_Ch3 <- results$slope
intercept_Ch3 <- results$intercept

results <- lm.slope.int(Exp64hi_Sorted, "Time", "Ch5")
slope_Ch5 <- results$slope
intercept_Ch5 <- results$intercept

results <- lm.slope.int(Exp64hi_Sorted, "Time", "Ch6")
slope_Ch6 <- results$slope
intercept_Ch6 <- results$intercept

results <- lm.slope.int(Exp64hi_Sorted, "Time", "Ch7")
slope_Ch7 <- results$slope
intercept_Ch7 <- results$intercept
```

Lines and y=mx+b
```{r}
ch022 <- (slope_ch0*20) + intercept_ch0
#ch035 <- (slope_ch0*24) + intercept_ch0

ch122 <- (slope_ch1*20) + intercept_ch1
#ch135 <- (slope_ch1*24) + intercept_ch1

ch222 <- (slope_ch2*20) + intercept_ch2
#ch235 <- (slope_ch2*24) + intercept_ch2

ch322 <- (slope_ch3*20) + intercept_ch3
#ch335 <- (slope_ch3*24) + intercept_ch3

ch522 <- (slope_ch5*20) + intercept_ch5
#ch535 <- (slope_ch5*24) + intercept_ch5

ch622 <- (slope_ch6*20) + intercept_ch6
#ch635 <- (slope_ch6*24) + intercept_ch6

ch722 <- (slope_ch7*20) + intercept_ch7
#ch735 <- (slope_ch7*24) + intercept_ch7


#Ch022 <- (slope_Ch0*31) + intercept_Ch0
Ch035 <- (slope_Ch0*35) + intercept_Ch0

#Ch122 <- (slope_Ch1*31) + intercept_Ch1
Ch135 <- (slope_Ch1*35) + intercept_Ch1

#Ch222 <- (slope_Ch2*31) + intercept_Ch2
Ch235 <- (slope_Ch2*35) + intercept_Ch2

#Ch322 <- (slope_Ch3*31) + intercept_Ch3
Ch335 <- (slope_Ch3*35) + intercept_Ch3

#Ch522 <- (slope_Ch5*31) + intercept_Ch5
Ch535 <- (slope_Ch5*35) + intercept_Ch5

#Ch622 <- (slope_Ch6*31) + intercept_Ch6
Ch635 <- (slope_Ch6*35) + intercept_Ch6

#Ch722 <- (slope_Ch7*31) + intercept_Ch7
Ch735 <- (slope_Ch7*35) + intercept_Ch7


#Ranges

ch0R <- Ch035 - ch022
ch1R <- Ch135 - ch122
ch2R <- Ch235 - ch222
ch3R <- Ch335 - ch322
ch5R <- Ch535 - ch522
ch6R <- Ch635 - ch622
ch7R <- Ch735 - ch722


```


New data frame of channels and UCGREF: 
```{r}

channels <- tibble(
  Temp = c(20, 35),
  UCGREF = c(UCGREFL, UCGREFH), 
  Ch0 = c(ch022, Ch035),
  Ch1 = c(ch122, Ch135), 
  Ch2 = c(ch222, Ch235), 
  Ch3 = c(ch322, Ch335), 
  Ch5 = c(ch522, Ch535), 
  Ch6 = c(ch622, Ch635), 
  Ch7 = c(ch722, Ch735),
)

write.csv(channels, "X and Y of PRE sensor correction.csv", row.names = FALSE)
```

Graphing corrected channel data:
```{r}
ggplot(channels, aes(x = Temp))+
  geom_point(aes(y = Ch0, color = "F8"))+
  geom_point(aes(y = Ch1, color = "F2"))+
  geom_point(aes(y = Ch2, color = "F6"))+
  geom_point(aes(y = Ch3, color = "F7"))+
  geom_point(aes(y = Ch5, color = "F3"))+
  geom_point(aes(y = Ch6, color = "F5"))+
  geom_point(aes(y = Ch7, color = "F4"))+
  geom_smooth(aes(y = Ch0), method = "lm", se = FALSE, color = "blue")+
  geom_smooth(aes(y = Ch1), method = "lm", se = FALSE, color = "green")+
  geom_smooth(aes(y = Ch2), method = "lm", se = FALSE, color = "orange")+
  geom_smooth(aes(y = Ch3), method = "lm", se = FALSE, color = "pink")+
  geom_smooth(aes(y = Ch5), method = "lm", se = FALSE, color = "red")+
  geom_smooth(aes(y = Ch6), method = "lm", se = FALSE, color = "aquamarine4")+
  geom_smooth(aes(y = Ch7), method = "lm", se = FALSE, color = "purple")+
  geom_smooth(aes(y = UCGREF), method = "lm", se = FALSE, color = "black")+
#  geom_point(aes(y = GrefC, color = "GrefC"))+
  geom_point(aes(y = UCGREF, color = "Ref Post"))+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Temperature (°C)", 
       y="Temperature (°C)", 
       color = "Sensor")+
  scale_color_manual(name = "Sensor", 
                     breaks = c('F8', 'F2', 'F6', 'F7', 'F3', 'F5', 'F4', 'Ref Post'), 
                     values = c('F8' = 'blue', 'F2' = 'green', 'F6' = 'orange', 'F7' = 'pink', 'F3' = 'red', 'F5' = 'aquamarine4', 'F4' = 'purple', 'Ref Post' = 'black'))+
  ggtitle("Corrected Channels")+
  theme_classic()


Pre_cal_sen <- ggplot(channels, aes(x = Temp))+
  geom_point(aes(y = Ch0, color = "1"))+
  geom_point(aes(y = Ch1, color = "2"))+
  geom_point(aes(y = Ch2, color = "3"))+
  geom_point(aes(y = Ch3, color = "4"))+
  geom_point(aes(y = Ch5, color = "5"))+
  geom_point(aes(y = Ch6, color = "6"))+
  geom_point(aes(y = Ch7, color = "7"))+
  geom_smooth(aes(y = Ch0), method = "lm", se = FALSE, color = "blue")+
  geom_smooth(aes(y = Ch1), method = "lm", se = FALSE, color = "green")+
  geom_smooth(aes(y = Ch2), method = "lm", se = FALSE, color = "orange")+
  geom_smooth(aes(y = Ch3), method = "lm", se = FALSE, color = "pink")+
  geom_smooth(aes(y = Ch5), method = "lm", se = FALSE, color = "red")+
  geom_smooth(aes(y = Ch6), method = "lm", se = FALSE, color = "aquamarine4")+
  geom_smooth(aes(y = Ch7), method = "lm", se = FALSE, color = "purple")+
  geom_smooth(aes(y = UCGREF), method = "lm", se = FALSE, color = "black")+
  geom_point(aes(y = UCGREF, color = "Reference"))+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Temperature (°C)", 
       y="Temperature (°C)", 
       color = "Sensor")+
  scale_color_manual(name = "Sensor Number", 
                     breaks = c('Reference', '1', '2', '3', '4', '5', '6', '7'), 
                     values = c('1' = 'blue', '2' = 'green', '3' = 'orange', '4' = 'pink', '5' = 'red', '6' = 'aquamarine4', '7' = 'purple', 'Reference' = 'black'))+
  ggtitle("Pre-Calibration")+
  theme_classic()

Pre_cal_sen

#ggsave("Pre Calibration Sensor.png", Pre_cal_sen, width = 15, height = 10, units = "cm")
```

Ultimate Channel Formualas THIS IS THE IMPORTANT ONES FOR THE EXPERIMENTAL DATA:
```{r}
Correctedch0 <- (((17.90360 - min(Exp64lo$ch0))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch0) - min(Exp64lo$ch0))) + min(Exp64lo$UCGref)

CorrectedCh0 <- (((27.05045 - min(Exp64lo$ch0))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch0) - min(Exp64lo$ch0))) + min(Exp64lo$UCGref)

Correctedch1 <- (((17.87000 - min(Exp64lo$ch1))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch1) - min(Exp64lo$ch1))) + min(Exp64lo$UCGref)

CorrectedCh1 <- (((27.04320 - min(Exp64lo$ch1))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch1) - min(Exp64lo$ch1))) + min(Exp64lo$UCGref)

Correctedch2 <- (((18.02625 - min(Exp64lo$ch2))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch2) - min(Exp64lo$ch2))) + min(Exp64lo$UCGref)

CorrectedCh2 <- (((27.23430 - min(Exp64lo$ch2))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch2) - min(Exp64lo$ch2))) + min(Exp64lo$UCGref)

Correctedch3 <- (((17.92890 - min(Exp64lo$ch3))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch3) - min(Exp64lo$ch3))) + min(Exp64lo$UCGref)

CorrectedCh3 <- (((27.04315 - min(Exp64lo$ch3))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch3) - min(Exp64lo$ch3))) + min(Exp64lo$UCGref)

Correctedch5 <- (((17.79905 - min(Exp64lo$ch5))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch5) - min(Exp64lo$ch5))) + min(Exp64lo$UCGref)

CorrectedCh5 <- (((26.82060 - min(Exp64lo$ch5))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch5) - min(Exp64lo$ch5))) + min(Exp64lo$UCGref)

Correctedch6 <- (((17.86050 - min(Exp64lo$ch6))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch6) - min(Exp64lo$ch6))) + min(Exp64lo$UCGref)

CorrectedCh6 <- (((27.25580 - min(Exp64lo$ch6))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch6) - min(Exp64lo$ch6))) + min(Exp64lo$UCGref)

Correctedch7 <- (((17.81760 - min(Exp64lo$ch7))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch7) - min(Exp64lo$ch7))) + min(Exp64lo$UCGref)

CorrectedCh7 <- (((27.21245 - min(Exp64lo$ch7))*((max(Exp64hi$UCGref)- min(Exp64lo$UCGref))))/(max(Exp64hi$Ch7) - min(Exp64lo$ch7))) + min(Exp64lo$UCGref)

UCGREFlo <- (((18.08115 - GREF22)*(NISTR))/GREFR) + NIST22
UCGREFhi <- (((27.17370 - GREF22)*(NISTR))/GREFR) + NIST22
```

Values into table:
```{r}

corrected <- tibble(
  Temp = c(20, 35),
  UCGREF = c(UCGREFlo, UCGREFhi), 
  Ch0 = c(Correctedch0, CorrectedCh0),
  Ch1 = c(Correctedch1, CorrectedCh1), 
  Ch2 = c(Correctedch2, CorrectedCh2), 
  Ch3 = c(Correctedch3, CorrectedCh3), 
  Ch5 = c(Correctedch5, CorrectedCh5), 
  Ch6 = c(Correctedch6, CorrectedCh6), 
  Ch7 = c(Correctedch7, CorrectedCh7),
)

#write.csv(corrected, "X and Y of post sensor correction.csv", row.names = FALSE)
```

```{r}
Post_cal_sen <- ggplot(corrected, aes(x = Temp))+
  geom_point(aes(y = Ch0, color = "1"))+
  geom_point(aes(y = Ch1, color = "2"))+
  geom_point(aes(y = Ch2, color = "3"))+
  geom_point(aes(y = Ch3, color = "4"))+
  geom_point(aes(y = Ch5, color = "5"))+
  geom_point(aes(y = Ch6, color = "6"))+
  geom_point(aes(y = Ch7, color = "7"))+
  geom_smooth(aes(y = Ch0), method = "lm", se = FALSE, color = "blue")+
  geom_smooth(aes(y = Ch1), method = "lm", se = FALSE, color = "green")+
  geom_smooth(aes(y = Ch2), method = "lm", se = FALSE, color = "orange")+
  geom_smooth(aes(y = Ch3), method = "lm", se = FALSE, color = "pink")+
  geom_smooth(aes(y = Ch5), method = "lm", se = FALSE, color = "red")+
  geom_smooth(aes(y = Ch6), method = "lm", se = FALSE, color = "aquamarine4")+
  geom_smooth(aes(y = Ch7), method = "lm", se = FALSE, color = "purple")+
  geom_smooth(aes(y = UCGREF), method = "lm", se = FALSE, color = "black")+
#  geom_point(aes(y = GrefC, color = "GrefC"))+
  geom_point(aes(y = UCGREF, color = "Reference"))+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Temperature (°C)", 
       y="Temperature (°C)", 
       color = "Sensor")+
  scale_color_manual(name = "Sensor Number", 
                     breaks = c('Reference', '1', '2', '3', '4', '5', '6', '7'), 
                     values = c('1' = 'blue', '2' = 'green', '3' = 'orange', '4' = 'pink', '5' = 'red', '6' = 'aquamarine4', '7' = 'purple', 'Reference' = 'black'))+
  ggtitle("Post-Calibration")+
  theme_classic()

Post_cal_sen

#ggsave("Post Calibration Sensor.png", Post_cal_sen, width = 15, height = 10, units = "cm")
```
Lines for sensors post calibration:
```{r}
results <- lm.slope.int(corrected, "Temp", "Ch0")
slope_Ch0C <- results$slope
intercept_Ch0C <- results$intercept

results <- lm.slope.int(corrected, "Temp", "Ch1")
slope_Ch1C <- results$slope
intercept_Ch1C <- results$intercept

results <- lm.slope.int(corrected, "Temp", "Ch2")
slope_Ch2C <- results$slope
intercept_Ch2C <- results$intercept

results <- lm.slope.int(corrected, "Temp", "Ch3")
slope_Ch3C <- results$slope
intercept_Ch3C <- results$intercept

results <- lm.slope.int(corrected, "Temp", "Ch5")
slope_Ch5C <- results$slope
intercept_Ch5C <- results$intercept

results <- lm.slope.int(corrected, "Temp", "Ch6")
slope_Ch6C <- results$slope
intercept_Ch6C <- results$intercept

results <- lm.slope.int(corrected, "Temp", "Ch7")
slope_Ch7C <- results$slope
intercept_Ch7C <- results$intercept

results <- lm.slope.int(corrected, "Temp", "UCGREF")
slope_UCGREFC <- results$slope
intercept_UCGREFC <- results$intercept
```

Making new dataframe with Post-Calibration equation values:
```{r}
Post_cal_equations <- tibble(
  Sensor = c(1, 2, 3, 4, 5, 6, 7, "Reference"),
  Slope = c(slope_Ch0C, slope_Ch1C, slope_Ch2C, slope_Ch3C, slope_Ch5C, slope_Ch6C, slope_Ch7C, slope_UCGREFC), 
  Intercept = c(intercept_Ch0C, intercept_Ch1C, intercept_Ch2C, intercept_Ch3C, intercept_Ch5C, intercept_Ch7C, intercept_Ch7C, intercept_UCGREFC)
)

#write.csv(Post_cal_equations, "slopes and intercepts of post-calibration lines", row.names = FALSE)
```


