---
title: "SLI Gref Sensor Calibration"
output: html_document
date: "2024-02-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(car)
library(dplyr)
library(ggplot2)
library(ggridges)
library(datasets)
library(magrittr)
library(svglite)

```

Functions to load:
```{r}
#Function for converting volts to Celsius:
#TMP36 Sensors
VtoC36 <- function(volts) {
  celsius <- (volts - 0.5) / 0.01
  return(celsius)}

#Cleaning data frame -- removing unnecessary characters, making columns numeric, and removing all NA's
cleanSLI <- function(d, a, b) {
  d <- as.data.frame(d)
  d[[a]] <- gsub("=", "", d[[a]])
  d[[a]] <- gsub(":", "", d[[a]])
  d[[b]] <- gsub(":", "", d[[b]])
  d[[a]] <- as.numeric(d[[a]])
  d[[b]] <- as.numeric(d[[b]])
  d <- na.omit(d)
  return(d)
}

#Adding an Elapsed Time column to data frame:
#TCHC 2 point calibration data 
add.time1.6 <- function(d) {
  increment <- 1.6
  num_rows <- nrow(d)
  Time <- seq(from = 0, by = increment, length.out = num_rows)
  d$Time <- Time
  return(d)
}

#Creating Linear Models and Saving Slope and Intercepts From Data
lm.slope.int <- function(d, x, y) {
  formula_str <- paste(y, "~", x)
  lm_form <- as.formula(formula_str)
  lm_d <- lm(lm_form, data = d)
  lmcoef <- coef(lm_d)
  slope_d <- lmcoef[x]
  intercept_d <- lmcoef["(Intercept)"]
  return(list(slope = slope_d, intercept = intercept_d))
}

```

Read in data sets:
```{r}

SLIL1 <- read.csv("Low Temp Calibration SLI.csv")
SLIH1 <- read.csv("High Temp Calibration SLI.csv")

```

Subset data for only the columns you need:
```{r}

SLIL1 <- SLIL1[, c("X.1", "X.3")]
SLIH1 <- SLIH1[, c("X.6", "X.8")] 

```

Cleaning:
```{r}

SLIL2 <- cleanSLI(SLIL1, "X.1", "X.3")
SLIH2 <- cleanSLI(SLIH1, "X.6", "X.8")

```


Changing names of headings:
```{r}

colnames(SLIL2)[1] <- "NIST"
colnames(SLIL2)[2] <- "Gref"


colnames(SLIH2)[1] <- "NIST"
colnames(SLIH2)[2] <- "Gref"

```

Creating new columns converting Volts to Celsius:
```{r}

SLIL2$GrefC <- VtoC36(SLIL2$Gref)

SLIH2$GrefC <- VtoC36(SLIH2$Gref)

```

Create a new data frame for sorting by NIST:
```{r}

#Low Temp
#subset the data so you only have NIST and Gref values 
SLIL3 <- SLIL2[, c("NIST", "GrefC")]

#order the data based on ascending NIST values
SLIL3_Sorted <- SLIL3[order(SLIL3$NIST), ]

#High Temp
#subset the data so you only have NIST and Gref values 
SLIH3 <- SLIH2[, c("NIST", "GrefC")]

#order the data based on ascending NIST values
SLIH3_Sorted <- SLIH3[order(SLIH3$NIST), ]

```

Add Elapsed Time:
```{r}

SLIL3_Sorted <- add.time1.6(SLIL3_Sorted)
SLIH3_Sorted <- add.time1.6(SLIH3_Sorted)
```

Graphing Sorted Data:
```{r}
Sort_NIST_lo36 <- ggplot(SLIL3_Sorted, aes(x = Time))+
  geom_point(aes(y = GrefC, color = "Gref"))+
  geom_point(aes(y = NIST, color = "NIST"))+
  geom_smooth(aes(y = GrefC), method = "lm", se = FALSE, color = "black")+
  geom_smooth(aes(y = NIST), method = "lm", se = FALSE, color = "black")+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Time (sec)", 
       y="Temperature (°C)",
       color = "Reference")+
  scale_color_manual(name = "Sensor",
                     breaks = c('NIST', 'Gref'),
                     values = c('Gref' = 'red', 'NIST' = 'gold4'))+ 
  ggtitle("SLI TMP 36 Low Temp Calibration Sorted by NIST")+
  theme_classic()

Sort_NIST_hi36 <- ggplot(SLIH3_Sorted, aes(x = Time))+
  geom_point(aes(y = GrefC, color = "Gref"))+
  geom_point(aes(y = NIST, color = "NIST"))+
  geom_smooth(aes(y = GrefC), method = "lm", se = FALSE, color = "black")+
  geom_smooth(aes(y = NIST), method = "lm", se = FALSE, color = "black")+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Time (sec)", 
       y="Temperature (°C)",
       color = "Reference")+
  scale_color_manual(name = "Sensor",
                     breaks = c('NIST', 'Gref'),
                     values = c('Gref' = 'red', 'NIST' = 'gold4'))+ 
  ggtitle("SLI TMP 36 High Temp Calibration Sorted by NIST")+
  theme_classic()

Sort_NIST_lo36
Sort_NIST_hi36

#ggsave("Sort_NIST_lo36.png", plot = Sort_NIST_lo36, width = 10, height = 6, dpi = 300)
#ggsave("Sort_NIST_hi36.png", plot = Sort_NIST_hi36, width = 10, height = 6, dpi = 300)
```


Slope and Intercept of the lines created in graphs:
```{r}

#making the models for the lm lines on above graph
results <- lm.slope.int(SLIL3_Sorted, "Time", "NIST")
slope_LNIST <- results$slope
intercept_LNIST <- results$intercept

results <- lm.slope.int(SLIH3_Sorted, "Time", "NIST")
slope_HNIST <- results$slope
intercept_HNIST <- results$intercept

results <- lm.slope.int(SLIL3_Sorted, "Time", "GrefC")
slope_LGref <- results$slope
intercept_LGref <- results$intercept

results <- lm.slope.int(SLIH3_Sorted, "Time", "GrefC")
slope_HGref <- results$slope
intercept_HGref <- results$intercept

```

Plug in 22 and 35 into y=mx+b from above:
```{r}
#LOW
NIST22 <- (slope_LNIST*22) + intercept_LNIST

GREF22 <- (slope_LGref*22) + intercept_LGref

#HIGH
NIST35 <- (slope_HNIST*35) + intercept_HNIST

GREF35 <- (slope_HGref*35) + intercept_HGref

#Ranges
NISTR <- NIST35 - NIST22
  
GREFR <- GREF35 - GREF22

```


Making new dataframe w these 4 points:
```{r}
T1T2 <- tibble(
  Temp = c(22, 35),
  CGref = c(GREF22, GREF35),
  CNIST = c(NIST22, NIST35)
)
```

Graph CNIST and CGREF:
```{r}
CNIST_CGref <- ggplot(T1T2, aes(x = Temp))+
  geom_point(aes(y = CGref, color = "Gref"))+
  geom_point(aes(y = CNIST, color = "NIST"))+
  geom_smooth(aes(y = CGref), method = "lm", se = FALSE, color = "red")+
  geom_smooth(aes(y = CNIST), method = "lm", se = FALSE, color = "gold4")+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Temperature (°C)", 
       y="Temperature (°C)",
       color = "Sensor")+
  scale_color_manual(name = "Sensor",
                     breaks = c('NIST', 'Gref'),
                     values = c('Gref' = 'red', 'NIST' = 'gold4'))+ 
  ggtitle("SLI TMP 36 Corrected NIST and Gref Values")+
  theme_classic()

CNIST_CGref

#ggsave("CNIST_CGref.png", plot = CNIST_CGref, width = 10, height = 6, dpi = 300)

```
Slope and Intercept of the lines created in graphs:
```{r}

#making the models for the lm lines on above graphs
results <- lm.slope.int(T1T2, "Temp", "CNIST")
slope_CNIST <- results$slope
intercept_CNIST <- results$intercept

results <- lm.slope.int(T1T2, "Temp", "CGref")
slope_CGref <- results$slope
intercept_CGref <- results$intercept

```


Finding Ultimate Gref formula:
```{r}

UCGREFL <- (((13.0138 - GREF22)*(NISTR))/GREFR) + NIST22

UCGREFH <- (((21.1121 - GREF22)*(NISTR))/GREFR) + NIST22

```

New table adding UCGREF:
```{r}

NIST.UCGREF <- tibble(
  Temp = c(22, 35),
  CNIST = c(NIST22, NIST35),
  UCGREF = c(UCGREFL, UCGREFH)
)

```

Graphing Corrected NIST and UCGREF:
```{r}

CNIST_UCGref <- ggplot(NIST.UCGREF, aes(x = Temp))+
  geom_point(aes(y = UCGREF, color = "Ref Post"))+
  geom_point(aes(y = CNIST, color = "NIST"))+
  geom_smooth(aes(y = UCGREF), method = "lm", se = FALSE, color = "black")+
  geom_smooth(aes(y = CNIST), method = "lm", se = FALSE, color = "gold4")+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Temperature (°C)", 
       y="Temperature (°C)",
       color = "Sensor")+
  scale_color_manual(name = "Sensor",
                     breaks = c('NIST', 'Ref Post'),
                     values = c('Ref Post' = 'black', 'NIST' = 'gold4'))+ 
  ggtitle("SLI TMP 36 Final Corrected NIST and Gref")+
  theme_classic()

CNIST_UCGref

#ggsave("CNIST_UCGref.png", plot = CNIST_UCGref, width = 10, height = 6, dpi = 300)
```
