---
title: "EDCR calibration SLI"
output: html_document
date: "2024-03-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(car)
library(dplyr)
library(ggplot2)
library(ggridges)
library(datasets)
library(magrittr)
library(svglite)

```

Functions to load:
```{r}
#Function for converting volts to Celsius:
#TMP36 Sensors
VtoC36 <- function(volts) {
  celsius <- (volts - 0.5) / 0.01
  return(celsius)}

#Cleaning data frame -- removing unnecessary characters, making columns numeric, and removing all NA's
clean <- function(d, a, b) {
  d <- as.data.frame(d)
  d[[a]] <- gsub(":", "", d[[a]])
  d[[b]] <- gsub(":", "", d[[b]])
  d[[a]] <- as.numeric(d[[a]])
  d[[b]] <- as.numeric(d[[b]])
  d <- na.omit(d)
  return(d)
}


#ECDR Calorimeter data
add.time31.6 <- function(d) {
  increment <- 31.6
  num_rows <- nrow(d)
  Time <- seq(from = 0, by = increment, length.out = num_rows)
  d$Time <- Time
  return(d)
}

#Creating Linear Models and Saving Slope and Intercepts From Data
lm.slope.int <- function(d, x, y) {
  formula_str <- paste(y, "~", x)
  lm_form <- as.formula(formula_str)
  lm_d <- lm(lm_form, data = d)
  lmcoef <- coef(lm_d)
  slope_d <- lmcoef[x]
  intercept_d <- lmcoef["(Intercept)"]
  return(list(slope = slope_d, intercept = intercept_d))
}

#Creating a function to remove 0 values from data set
remove.zeros36 <- function(d, ...) {
  d %>%
    filter(across(..., ~ . > 0.5 & . < 0.9))
}


```

Read in data sets:
```{r}

SLIsencallo <- read.csv("SLIcal_Lo_022724.csv")
SLIsencalhi <- read.csv("SLIcal_Hi_030224.csv")

```

Subset for columns needed:
```{r}
SLIsencallo <- SLIsencallo[, c("ch0", "ch1", "ch2", "ch5", "ch6", "Gref")]
SLIsencalhi <- SLIsencalhi[, c("Ch0", "Ch1", "Ch2", "Ch5", "Ch6", "GrefAvg")]
```

Removing zeros:
```{r}
SLIsencallo <- subset(SLIsencallo, ch0 > 0.5)
SLIsencallo <- subset(SLIsencallo, ch1 > 0.5)
SLIsencallo <- subset(SLIsencallo, ch2 > 0.5)
SLIsencallo <- subset(SLIsencallo, ch5 > 0.5)
SLIsencallo <- subset(SLIsencallo, ch6 > 0.5)

SLIsencalhi <- subset(SLIsencalhi, Ch0 < 0.9)
SLIsencalhi <- subset(SLIsencalhi, Ch1 < 0.9)
SLIsencalhi <- subset(SLIsencalhi, Ch2 < 0.9)
SLIsencalhi <- subset(SLIsencalhi, Ch5 < 0.9)
SLIsencalhi <- subset(SLIsencalhi, Ch6 < 0.9)
```


Add Elapsed Time to new sorted data frame:
```{r}

SLIsencallo <- add.time31.6(SLIsencallo)
SLIsencalhi <- add.time31.6(SLIsencalhi)

```

Celsius:
```{r}
SLIsencallo$ch0C <- VtoC36(SLIsencallo$ch0)
SLIsencallo$ch1C <- VtoC36(SLIsencallo$ch1)
SLIsencallo$ch2C <- VtoC36(SLIsencallo$ch2)
SLIsencallo$ch5C <- VtoC36(SLIsencallo$ch5)
SLIsencallo$ch6C <- VtoC36(SLIsencallo$ch6)

SLIsencalhi$Ch0C <- VtoC36(SLIsencalhi$Ch0)
SLIsencalhi$Ch1C <- VtoC36(SLIsencalhi$Ch1)
SLIsencalhi$Ch2C <- VtoC36(SLIsencalhi$Ch2)
SLIsencalhi$Ch5C <- VtoC36(SLIsencalhi$Ch5)
SLIsencalhi$Ch6C <- VtoC36(SLIsencalhi$Ch6)

SLIsencallo$GrefC <- VtoC36(SLIsencallo$Gref)
SLIsencalhi$GrefC <- VtoC36(SLIsencalhi$GrefAvg)
```

Column for UCGref:
```{r}

SLIsencallo$UCGref <- ((((SLIsencallo$GrefC - GREF22)*(NISTR))/GREFR) + NIST22)
SLIsencalhi$UCGref <- ((((SLIsencalhi$GrefC - GREF22)*(NISTR))/GREFR) + NIST22)

```

Graphing unsorted data:
```{r}
#ggplot(SLIsencallo, aes(x = Time))+
#  geom_point(aes(y = ch0C, color = "ch0"))+
#  geom_point(aes(y = ch1C, color = "ch1"))+
#  geom_point(aes(y = ch2C, color = "ch2"))+
#  geom_point(aes(y = ch5C, color = "ch5"))+
#  geom_point(aes(y = ch6C, color = "ch6"))+
##  geom_point(aes(y = GrefC, color = "GrefC"))+
#  geom_point(aes(y = UCGref, color = "UCGref"))+
#  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
#  labs(x="Time (sec)", 
#       y="Temperature (degrees C)", 
#       color = "Reference")+
#  scale_color_manual(name = "Reference", 
#                     breaks = c('ch0', 'ch1', 'ch2', 'ch5', 'ch6', 'GrefC', 'UCGref'), 
#                     values = c('ch0' = 'blue', 'ch1' = 'green', 'ch2' = 'gold', 'ch5' = 'red', 'ch6' = 'black', 'GrefC' = #'purple', 'UCGref' = 'gold4'))+
#  ggtitle("Low Temperature EDCR SLI")+
#  theme_classic()
#
#ggplot(SLIsencalhi, aes(x = Time))+
#  geom_point(aes(y = Ch0C, color = "Ch0"))+
#  geom_point(aes(y = Ch1C, color = "Ch1"))+
#  geom_point(aes(y = Ch2C, color = "Ch2"))+
#  geom_point(aes(y = Ch5C, color = "Ch5"))+
#  geom_point(aes(y = Ch6C, color = "Ch6"))+
##  geom_point(aes(y = GrefC, color = "GrefC"))+
#  geom_point(aes(y = UCGref, color = "UCGref"))+
#  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
#  labs(x="Time (sec)", 
#       y="Temperature (degrees C)", 
#       color = "Reference")+
#  scale_color_manual(name = "Reference", 
#                     breaks = c('Ch0', 'Ch1', 'Ch2', 'Ch5', 'Ch6', 'GrefC', 'UCGref'), 
#                     values = c('Ch0' = 'blue', 'Ch1' = 'green', 'Ch2' = 'gold', 'Ch5' = 'red', 'Ch6' = 'black', 'GrefC' = #'purple', 'UCGref' = 'gold4'))+
#  ggtitle("High Temp EDCR SLI")+
#  theme_classic()
```

Sort data by UCGREF:
```{r}

#order the data based on ascending NIST values
SLIsencallo_Sorted <- SLIsencallo[order(SLIsencallo$UCGref), ]

#order the data based on ascending NIST values
SLIsencalhi_Sorted <- SLIsencalhi[order(SLIsencalhi$UCGref), ]

```

Add Elapsed Time to new data frame:
```{r}
SLIsencallo_Sorted <- add.time31.6(SLIsencallo_Sorted)
SLIsencalhi_Sorted <- add.time31.6(SLIsencalhi_Sorted)
```

Graphing Sorted data:
```{r}
SLIch_Sortedlo <- ggplot(SLIsencallo_Sorted, aes(x = Time))+
  geom_point(aes(y = ch0C, color = "D4"))+
  geom_point(aes(y = ch1C, color = "D6"))+
  geom_point(aes(y = ch2C, color = "D2"))+
  geom_point(aes(y = ch5C, color = "D7"))+
  geom_point(aes(y = ch6C, color = "D8"))+
#  geom_point(aes(y = GrefC, color = "GrefC"))+
 # geom_point(aes(y = UCGref, color = "UCGref"))+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Time (s)", 
       y="Temperature (°C)", 
       color = "Sensor")+
  scale_color_manual(name = "Sensor", 
                     breaks = c('D2', 'D4', 'D6', 'D7', 'D8', 'UCGref'), 
                     values = c('D2' = 'maroon2', 'D4' = 'royalblue3', 'D6' = 'seagreen2', 'D7' = 'sienna2', 'D8' = 'slategrey', 'UCGref' = 'black'))+
  ggtitle("SLI Low Temp Sorted by Corrected Gref")+
  theme_classic()

SLIch_Sortedhi <- ggplot(SLIsencalhi_Sorted, aes(x = Time))+
  geom_point(aes(y = Ch0C, color = "D4"))+
  geom_point(aes(y = Ch1C, color = "D6"))+
  geom_point(aes(y = Ch2C, color = "D2"))+
  geom_point(aes(y = Ch5C, color = "D7"))+
  geom_point(aes(y = Ch6C, color = "D8"))+
#  geom_point(aes(y = GrefC, color = "GrefC"))+
  #geom_point(aes(y = UCGref, color = "UCGref"))+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Time (s)", 
       y="Temperature (°C)", 
       color = "Sensor")+
  scale_color_manual(name = "Sensor", 
                     breaks = c('D2', 'D4', 'D6', 'D7', 'D8', 'UCGref'), 
                     values = c('D2' = 'maroon2', 'D4' = 'royalblue3', 'D6' = 'seagreen2', 'D7' = 'sienna2', 'D8' = 'slategrey', 'UCGref' = 'black'))+
  ggtitle("SLI High Temp Sorted by Corrected Gref")+
  theme_classic()

SLIch_Sortedlo
SLIch_Sortedhi

#ggsave("SLIch_Sortedlo.png", plot = SLIch_Sortedlo, width = 10, height = 6, dpi = 300)
#ggsave("SLIch_Sortedhi.png", plot = SLIch_Sortedhi, width = 10, height = 6, dpi = 300)
```

Slope and Intercept of the lines created in graphs:
```{r}

#making the models for the lm lines on above graph
results <- lm.slope.int(SLIsencallo_Sorted, "Time", "ch0C")
slope_ch0 <- results$slope
intercept_ch0 <- results$intercept

results <- lm.slope.int(SLIsencallo_Sorted, "Time", "ch1C")
slope_ch1 <- results$slope
intercept_ch1 <- results$intercept

results <- lm.slope.int(SLIsencallo_Sorted, "Time", "ch2C")
slope_ch2 <- results$slope
intercept_ch2 <- results$intercept

results <- lm.slope.int(SLIsencallo_Sorted, "Time", "ch5C")
slope_ch5 <- results$slope
intercept_ch5 <- results$intercept

results <- lm.slope.int(SLIsencallo_Sorted, "Time", "ch6C")
slope_ch6 <- results$slope
intercept_ch6 <- results$intercept



results <- lm.slope.int(SLIsencalhi_Sorted, "Time", "Ch0C")
slope_Ch0 <- results$slope
intercept_Ch0 <- results$intercept

results <- lm.slope.int(SLIsencalhi_Sorted, "Time", "Ch1C")
slope_Ch1 <- results$slope
intercept_Ch1 <- results$intercept

results <- lm.slope.int(SLIsencalhi_Sorted, "Time", "Ch2C")
slope_Ch2 <- results$slope
intercept_Ch2 <- results$intercept

results <- lm.slope.int(SLIsencalhi_Sorted, "Time", "Ch5C")
slope_Ch5 <- results$slope
intercept_Ch5 <- results$intercept

results <- lm.slope.int(SLIsencalhi_Sorted, "Time", "Ch6C")
slope_Ch6 <- results$slope
intercept_Ch6 <- results$intercept

```


Lines and y=mx+b
```{r}
ch022 <- (slope_ch0*20) + intercept_ch0

ch122 <- (slope_ch1*20) + intercept_ch1

ch222 <- (slope_ch2*20) + intercept_ch2

ch522 <- (slope_ch5*20) + intercept_ch5

ch622 <- (slope_ch6*20) + intercept_ch6


Ch035 <- (slope_Ch0*35) + intercept_Ch0

Ch135 <- (slope_Ch1*35) + intercept_Ch1

Ch235 <- (slope_Ch2*35) + intercept_Ch2

Ch535 <- (slope_Ch5*35) + intercept_Ch5

Ch635 <- (slope_Ch6*35) + intercept_Ch6



#Ranges

ch0R <- Ch035 - ch022
ch1R <- Ch135 - ch122
ch2R <- Ch235 - ch222
ch5R <- Ch535 - ch522
ch6R <- Ch635 - ch622


```

New data frame of channels and UCGREF: 
```{r}

channels <- tibble(
  Temp = c(20, 35),
  UCGREF = c(UCGREFL, UCGREFH), 
  Ch0 = c(ch022, Ch035),
  Ch1 = c(ch122, Ch135), 
  Ch2 = c(ch222, Ch235), 
  Ch5 = c(ch522, Ch535), 
  Ch6 = c(ch622, Ch635), 
)
```

Graphing corrected channel data:
```{r}
SLIcorrectedsen <- ggplot(channels, aes(x = Temp))+
  geom_point(aes(y = Ch0, color = "D4"))+
  geom_point(aes(y = Ch1, color = "D6"))+
  geom_point(aes(y = Ch2, color = "D2"))+
  geom_point(aes(y = Ch5, color = "D7"))+
  geom_point(aes(y = Ch6, color = "D8"))+
  geom_smooth(aes(y = Ch0), method = "lm", se = FALSE, color = "royalblue3")+
  geom_smooth(aes(y = Ch1), method = "lm", se = FALSE, color = "seagreen2")+
  geom_smooth(aes(y = Ch2), method = "lm", se = FALSE, color = "maroon2")+
  geom_smooth(aes(y = Ch5), method = "lm", se = FALSE, color = "sienna2")+
  geom_smooth(aes(y = Ch6), method = "lm", se = FALSE, color = "slategrey")+
  geom_smooth(aes(y = UCGREF), method = "lm", se = FALSE, color = "black")+
#  geom_point(aes(y = GrefC, color = "GrefC"))+
  geom_point(aes(y = UCGREF, color = "Reference"))+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Temperature (°C)", 
       y="Temperature (°C)", 
       color = "Sensor")+
  scale_color_manual(name = "Sensor", 
                     breaks = c('Reference', 'D2', 'D4', 'D6', 'D7', 'D8'), 
                     values = c('D2' = 'maroon2', 'D4' = 'royalblue3', 'D6' = 'seagreen2', 'D7' = 'sienna2', 'D8' = 'slategrey', 'Reference' = 'black'))+
  ggtitle("SLI TMP 36 Corrected Sensors")+
  theme_classic()

SLIcorrectedsen

#ggsave("SLIcorrectedsen.png", plot = SLIcorrectedsen, width = 10, height = 6, dpi = 300)

```


Ultimate Channel Formualas THIS IS THE IMPORTANT ONES FOR THE EXPERIMENTAL DATA:
~Raw data taken from SLsIsencallo and hi, first row of each respective one~
```{r}
Correctedch0 <- (((15.0020 - min(SLIsencallo$ch0C))*((max(SLIsencalhi$UCGref)- min(SLIsencallo$UCGref))))/(max(SLIsencalhi$Ch0C) - min(SLIsencallo$ch0C))) + min(SLIsencallo$UCGref)

CorrectedCh0 <- (((22.3566 - min(SLIsencallo$ch0C))*((max(SLIsencalhi$UCGref)- min(SLIsencallo$UCGref))))/(max(SLIsencalhi$Ch0C) - min(SLIsencallo$ch0C))) + min(SLIsencallo$UCGref)

Correctedch1 <- (((14.7437 - min(SLIsencallo$ch1C))*((max(SLIsencalhi$UCGref)- min(SLIsencallo$UCGref))))/(max(SLIsencalhi$Ch1C) - min(SLIsencallo$ch1C))) + min(SLIsencallo$UCGref)

CorrectedCh1 <- (((22.2223 - min(SLIsencallo$ch1C))*((max(SLIsencalhi$UCGref)- min(SLIsencallo$UCGref))))/(max(SLIsencalhi$Ch1C) - min(SLIsencallo$ch1C))) + min(SLIsencallo$UCGref)

Correctedch2 <- (((14.8363 - min(SLIsencallo$ch2C))*((max(SLIsencalhi$UCGref)- min(SLIsencallo$UCGref))))/(max(SLIsencalhi$Ch2C) - min(SLIsencallo$ch2C))) + min(SLIsencallo$UCGref)

CorrectedCh2 <- (((22.2086 - min(SLIsencallo$ch2C))*((max(SLIsencalhi$UCGref)- min(SLIsencallo$UCGref))))/(max(SLIsencalhi$Ch2C) - min(SLIsencallo$ch2C))) + min(SLIsencallo$UCGref)

Correctedch5 <- (((15.2776 - min(SLIsencallo$ch5C))*((max(SLIsencalhi$UCGref)- min(SLIsencallo$UCGref))))/(max(SLIsencalhi$Ch5C) - min(SLIsencallo$ch5C))) + min(SLIsencallo$UCGref)

CorrectedCh5 <- (((22.5029 - min(SLIsencallo$ch5C))*((max(SLIsencalhi$UCGref)- min(SLIsencallo$UCGref))))/(max(SLIsencalhi$Ch5C) - min(SLIsencallo$ch5C))) + min(SLIsencallo$UCGref)

Correctedch6 <- (((15.0158 - min(SLIsencallo$ch6C))*((max(SLIsencalhi$UCGref)- min(SLIsencallo$UCGref))))/(max(SLIsencalhi$Ch6C) - min(SLIsencallo$ch6C))) + min(SLIsencallo$UCGref)

CorrectedCh6 <- (((21.9900 - min(SLIsencallo$ch6C))*((max(SLIsencalhi$UCGref)- min(SLIsencallo$UCGref))))/(max(SLIsencalhi$Ch6C) - min(SLIsencallo$ch6C))) + min(SLIsencallo$UCGref)

UCGREFlo <- (((13.17211 - GREF22)*(NISTR))/GREFR) + NIST22
UCGREFhi <- (((21.28410 - GREF22)*(NISTR))/GREFR) + NIST22
```

Values into a table:
```{r}

corrected <- tibble(
  Temp = c(20, 35),
  UCGREF = c(UCGREFlo, UCGREFhi), 
  Ch0 = c(Correctedch0, CorrectedCh0),
  Ch1 = c(Correctedch1, CorrectedCh1), 
  Ch2 = c(Correctedch2, CorrectedCh2), 
  Ch5 = c(Correctedch5, CorrectedCh5), 
  Ch6 = c(Correctedch6, CorrectedCh6), 
)
```

Plotting Corrected Values:
```{r}
SLIfinalcorrectedsen <- ggplot(corrected, aes(x = Temp))+
  geom_point(aes(y = Ch0, color = "D4"))+
  geom_point(aes(y = Ch1, color = "D6"))+
  geom_point(aes(y = Ch2, color = "D2"))+
  geom_point(aes(y = Ch5, color = "D7"))+
  geom_point(aes(y = Ch6, color = "D8"))+
  geom_point(aes(y = UCGREF, color = "Reference"))+
  geom_smooth(aes(y = Ch0), method = "lm", se = FALSE, color = "royalblue3")+
  geom_smooth(aes(y = Ch1), method = "lm", se = FALSE, color = "seagreen2")+
  geom_smooth(aes(y = Ch2), method = "lm", se = FALSE, color = "maroon2")+
  geom_smooth(aes(y = Ch5), method = "lm", se = FALSE, color = "sienna2")+
  geom_smooth(aes(y = Ch6), method = "lm", se = FALSE, color = "slategrey")+
  geom_smooth(aes(y = UCGREF), method = "lm", se = FALSE, color = "black")+
#  geom_point(aes(y = GrefC, color = "GrefC"))+
  geom_point(aes(y = UCGREF, color = "UCGref"))+
  scale_x_continuous(breaks = scales::pretty_breaks(n=10))+
  labs(x="Temperature (°C)", 
       y="Temperature (°C)", 
       color = "Sensor")+
  scale_color_manual(name = "Sensor", 
                     breaks = c('Reference', 'D2', 'D4', 'D6', 'D7', 'D8'), 
                     values = c('D2' = 'maroon2', 'D4' = 'royalblue3', 'D6' = 'seagreen2', 'D7' = 'sienna2', 'D8' = 'slategrey', 'Reference' = 'black'))+
  ggtitle("SLI TMP 36 Final Corrected Sensors")+
  theme_classic()

SLIfinalcorrectedsen

#ggsave("SLIfinalcorrectedsen.png", plot = SLIfinalcorrectedsen, width = 10, height = 6, dpi = 300)
```


~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#Make line from ex: x = 500 to 1000 for each channel. Tell range of y for your choosing. 

Standard Deviation from UCGREF and percent error:
```{r}
SD_lo <- sd(SLIsencallo$UCGref)
SD_hi <- sd(SLIsencalhi$UCGref)


SLIsencallo$PercentErrorch0 <- abs((SLIsencallo$ch0Corrected - SLIsencallo$UCGref) / SLIsencallo$ch0Corrected) * 100
SLIsencallo$PercentErrorch1 <- abs((SLIsencallo$ch1Corrected - SLIsencallo$UCGref) / SLIsencallo$ch1Corrected) * 100
SLIsencallo$PercentErrorch2 <- abs((SLIsencallo$ch2Corrected - SLIsencallo$UCGref) / SLIsencallo$ch2Corrected) * 100
SLIsencallo$PercentErrorch5 <- abs((SLIsencallo$ch5Corrected - SLIsencallo$UCGref) / SLIsencallo$ch5Corrected) * 100
SLIsencallo$PercentErrorch6 <- abs((SLIsencallo$ch6Corrected - SLIsencallo$UCGref) / SLIsencallo$ch6Corrected) * 100

SLIsencalhi$PercentErrorCh0 <- abs((SLIsencalhi$Ch0Corrected - SLIsencalhi$UCGref) / SLIsencalhi$Ch0Corrected) * 100
SLIsencalhi$PercentErrorCh1 <- abs((SLIsencalhi$Ch1Corrected - SLIsencalhi$UCGref) / SLIsencalhi$Ch1Corrected) * 100
SLIsencalhi$PercentErrorCh2 <- abs((SLIsencalhi$Ch2Corrected - SLIsencalhi$UCGref) / SLIsencalhi$Ch2Corrected) * 100
SLIsencalhi$PercentErrorCh5 <- abs((SLIsencalhi$Ch5Corrected - SLIsencalhi$UCGref) / SLIsencalhi$Ch5Corrected) * 100
SLIsencalhi$PercentErrorCh6 <- abs((SLIsencalhi$Ch6Corrected - SLIsencalhi$UCGref) / SLIsencalhi$Ch6Corrected) * 100

ch0_mean <- mean(SLIsencallo$PercentErrorch0) 
ch1_mean <- mean(SLIsencallo$PercentErrorch1)
ch2_mean <- mean(SLIsencallo$PercentErrorch2)
ch5_mean <- mean(SLIsencallo$PercentErrorch5)
ch6_mean <- mean(SLIsencallo$PercentErrorch6)

Ch0_mean <- mean(SLIsencalhi$PercentErrorCh0)
Ch1_mean <- mean(SLIsencalhi$PercentErrorCh1)
Ch2_mean <- mean(SLIsencalhi$PercentErrorCh2)
Ch5_mean <- mean(SLIsencalhi$PercentErrorCh5)
Ch6_mean <- mean(SLIsencalhi$PercentErrorCh6)

print(ch0_mean)
print(ch1_mean)
print(ch2_mean)
print(ch5_mean)
print(ch6_mean)

print(Ch0_mean)
print(Ch1_mean)
print(Ch2_mean)
print(Ch5_mean)
print(Ch6_mean)

print(SD_lo)
print(SD_hi)

#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

SLIsencallo$PercentErrorch0R <- abs((SLIsencallo$ch0C - SLIsencallo$UCGref) / SLIsencallo$ch0C) * 100
SLIsencallo$PercentErrorch1R <- abs((SLIsencallo$ch1C - SLIsencallo$UCGref) / SLIsencallo$ch1C) * 100
SLIsencallo$PercentErrorch2R <- abs((SLIsencallo$ch2C - SLIsencallo$UCGref) / SLIsencallo$ch2C) * 100
SLIsencallo$PercentErrorch5R <- abs((SLIsencallo$ch5C - SLIsencallo$UCGref) / SLIsencallo$ch5C) * 100
SLIsencallo$PercentErrorch6R <- abs((SLIsencallo$ch6C - SLIsencallo$UCGref) / SLIsencallo$ch6C) * 100

SLIsencalhi$PercentErrorCh0R <- abs((SLIsencalhi$Ch0C - SLIsencalhi$UCGref) / SLIsencalhi$Ch0C) * 100
SLIsencalhi$PercentErrorCh1R <- abs((SLIsencalhi$Ch1C - SLIsencalhi$UCGref) / SLIsencalhi$Ch1C) * 100
SLIsencalhi$PercentErrorCh2R <- abs((SLIsencalhi$Ch2C - SLIsencalhi$UCGref) / SLIsencalhi$Ch2C) * 100
SLIsencalhi$PercentErrorCh5R <- abs((SLIsencalhi$Ch5C - SLIsencalhi$UCGref) / SLIsencalhi$Ch5C) * 100
SLIsencalhi$PercentErrorCh6R <- abs((SLIsencalhi$Ch6C - SLIsencalhi$UCGref) / SLIsencalhi$Ch6C) * 100

ch0_meanR <- mean(SLIsencallo$PercentErrorch0R) 
ch1_meanR <- mean(SLIsencallo$PercentErrorch1R)
ch2_meanR <- mean(SLIsencallo$PercentErrorch2R)
ch5_meanR <- mean(SLIsencallo$PercentErrorch5R)
ch6_meanR <- mean(SLIsencallo$PercentErrorch6R)

Ch0_meanR <- mean(SLIsencalhi$PercentErrorCh0R)
Ch1_meanR <- mean(SLIsencalhi$PercentErrorCh1R)
Ch2_meanR <- mean(SLIsencalhi$PercentErrorCh2R)
Ch5_meanR <- mean(SLIsencalhi$PercentErrorCh5R)
Ch6_meanR <- mean(SLIsencalhi$PercentErrorCh6R)

print(ch0_meanR)
print(ch1_meanR)
print(ch2_meanR)
print(ch5_meanR)
print(ch6_meanR)

print(Ch0_meanR)
print(Ch1_meanR)
print(Ch2_meanR)
print(Ch5_meanR)
print(Ch6_meanR)
```





